Relict deciduous oaks show high resilience to drought despite the effect of land-use legacies

### 2019-06-26 man/figures/resilience_long_term.Rmd
update figure 6

  eq2 <- substitute(~~italic(r)^2~"="~rvalue*","~italic(p)~"="~pvalue,  
                    list(rvalue = format(summary(m)$r.squared, digits = 3), 
                         pvalue = format(summary(m)$coefficients[2,4], digits = 3)))

@@

```{r}
library("purrr")

sdfsite <- df %>% 
  filter(samps >= 10) %>% 
  group_by(disturb_year, site) %>% 
  filter(disturb_year > 1950) %>% 
  summarise_at(c("rt_mean", "rs_mean", "rc_mean", "rrs_mean"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  inner_join(dy, by=c("disturb_year" = "maxyear"))

@@

  ggplot(df, 
         aes_string(y=paste0(v, "_mean_mean"), x=x, label=label, colour=site, fill=site)) +
    geom_smooth(method='lm', se=FALSE, aes(group=1), colour='gray',  size = 1) + # linetype = "dotted",
    geom_smooth(method='lm', se=FALSE) + 
    geom_point(size=1.5, pch = 21) + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 2, show.legend = FALSE) + 
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10)) +
    geom_text_repel(data = eqns, aes(x = coord_eqX, y = Inf, label = equation), 
                    direction = "y", 
                    parse = TRUE, segment.size = 0, show.legend = FALSE)

@@

```{r}
sevRt_site <- plotrelsite(sdfsite, v = "rt", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rt", coord_eqX = Inf) +
  xlab('') + ylab('') + xlim(5,25)

# + theme(plot.margin = margin(r=-0.7, l=0, t=0, b=0, "pt"))
```

```{r}
sevRs_site <- plotrelsite(sdfsite, v = "rs", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rs", coord_eqX = -Inf) + xlab('') + ylab('') + xlim(5,25)
# theme(plot.margin = margin(r=0, l=-0.7, t=0, b=0, "pt")) 
```

```{r}
sevRc_site <- plotrelsite(sdfsite, v = "rc", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rc",  coord_eqX = -Inf) +
  xlab("Drought Severity") + ylab("") + xlim(5,25)
#+ theme(plot.margin = margin(r=-0.7, l=-0.7, t=0, b=0, "pt"))
```

@@

ggsave(filename = here::here("./man/figures/svg/fig_6.jpg"), 
       dpi = 300,  plot=res_long_term_sites, width=9, height=7)

@@

>>>>

  eq2 <- substitute(~~italic(r)^2~"="~rvalue*","~italic(p)~"="~pvalue,  
                    list(rvalue = formatC(summary(m)$r.squared, digits = 3, format = "f"), 
                         pvalue = formatC(summary(m)$coefficients[2,4], digits = 3, format = "f")))

@@

```{r}
# Plot separately 
library("purrr")

@@

  ggplot(df, 
         aes_string(y=paste0(v, "_mean_mean"), x=x, label=label, colour=site, fill=site)) +
    geom_smooth(method='lm', se=FALSE, aes(group=1), colour='gray',  size = 1) + # linetype = "dotted",
    geom_smooth(method='lm', se=FALSE) + 
    geom_point(size=1.5, pch = 21) + 
    theme_bw() + 
    geom_text_repel(nudge_x = 0.5, size = 2, show.legend = FALSE) + 
    ggtitle(titulo) + 
    theme(plot.title = element_text(size = 11, face = "bold.italic"),
          panel.grid = element_blank(), 
          axis.text.y = element_text(size=9),
          axis.text.x = element_text(size=9),
          axis.title = element_text(size = 10)) +
    geom_text_repel(data = eqns, aes(x = coord_eqX, y = Inf, label = equation),
                    direction = "y", segment.size = 0, hjust = 0,
                    parse = TRUE, show.legend = FALSE)
}

@@

```{r}
# Include 1995
sdfsite <- df %>% 
  filter(samps >= 10) %>% 
  group_by(disturb_year, site) %>% 
  filter(disturb_year > 1940) %>% 
  summarise_at(c("rt_mean", "rs_mean", "rc_mean", "rrs_mean"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  inner_join(dy, by=c("disturb_year" = "maxyear"))

v = "rt"
x = 'd_severity'
formulita <- as.formula(paste0(v, "_mean_mean ~", x))

  eqns <- sdfsite %>% split(.$site) %>% 
    map(~ lm(formulita, data = .)) %>%
    map(lm_eqn) %>% 
    do.call(rbind, .) %>%
    as.data.frame() %>%
    set_names("equation") %>%
    mutate(site = rownames(.))

sevRt_site <- plotrelsite(sdfsite, v = "rt", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rt", coord_eqX = Inf) + xlab('') + ylab('') + xlim(5,25)

sevRs_site <- plotrelsite(sdfsite, v = "rs", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rs", coord_eqX = -Inf) + xlab('') + ylab('') + xlim(5,25)

sevRc_site <- plotrelsite(sdfsite, v = "rc", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rc",  coord_eqX = -Inf) +
  xlab("Drought Severity") + ylab("") + xlim(5,25)

@@

ggsave(filename = here::here("./man/figures/svg/fig_6.jpg"), 
       dpi = 300,  plot=res_long_term_sites, width=8.5, height=7)

@@

```{r no95}
sdfsite95 <- df %>% 
  filter(samps >= 5) %>% 
  group_by(disturb_year, site) %>% 
  filter(disturb_year > 1940) %>% 
  filter(disturb_year != 1995) %>% 
  summarise_at(c("rt_mean", "rs_mean", "rc_mean", "rrs_mean"), 
               funs(mean(., na.rm = TRUE), sd(., na.rm=TRUE),se=sd(., na.rm=TRUE)/sqrt(n()))) %>% 
  inner_join(dy, by=c("disturb_year" = "maxyear"))

sevRt_site95 <- plotrelsite(sdfsite95, v = "rt", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rt", coord_eqX = Inf) + xlab('') + ylab('')

sevRs_site95 <- plotrelsite(sdfsite95, v = "rs", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rs", coord_eqX = -Inf) + xlab('') + ylab('')

sevRc_site95 <- plotrelsite(sdfsite95, v = "rc", x = 'd_severity', label = 'disturb_year', site = "site",
                 titulo = "Rc",  coord_eqX = -Inf) + xlab("Drought Severity") + ylab("")

res_long_term_sites95 <- sevRt_site95 + theme(legend.position="none") +
  sevRc_site95 + theme(legend.position="bottom") +
  sevRs_site95 + theme(legend.position = "none") + plot_layout(nrow = 1)

ggsave(filename = here::here("./man/figures/svg/fig_6_95.jpg"), 
       dpi = 300,  plot=res_long_term_sites95, width=9, height=7)

```{r, fig.width=6, dpi = 300, out.width = 0.8}
res_long_term_sites95
```
